Scikit-learn: API design for machine learning

### 2013-06-18 paper.tex
Cosmit.

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows.

>>>>

As the above example shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
